Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-09-08 Manuscript/HI_Model_ms.Rmd
updated manuscript files

```{r fig.align = 'center', out.width = "95%", fig.cap = "Land cover classification of the seven main Hawaiian Islands, adapted from Jacobi et al (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Water and Wetland land cover classes are not shown."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png")
```

@@

## Results
 Terrestrial ecosystems of the seven main Hawaiian Islands stored an estimated 316 Tg of carbon at the beginning of the simulation period in 2010, with 58% in soil organic matter, 22% in living biomass, and 20% in surface dead organic matter (litter and dead wood; Fig. 2a). The combination of low radiative forcing and low land use change yielded the highest and most consistent projections of ecosystem carbon accumulation, with a gain of ~15% to an average of 363 Tg of carbon by 2100 (Fig. 2a).

```{r fig.align = 'center', out.width = "95%", fig.cap = "Projected changes in total ecosystem carbon storage (a) and individual carbon stocks (b) for the seven main Hawaiian Islands. Solid lines indicate the mean of 30 Monte Carlo realizations for each scenario, with shaded areas indicating the minimum and maximum range of Monte Carlo realizations."}
knitr::include_graphics("./fig_images/fig2_Cstocks.png")
```

>>>>

```{r fig.align = 'center', out.width = "99%", fig.cap = "Land cover classification of the seven main Hawaiian Islands, adapted from Jacobi et al (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Water and Wetland land cover classes are not shown."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png")
```

@@

## Results
 Terrestrial ecosystems of the seven main Hawaiian Islands stored an estimated 316 Tg of carbon at the beginning of the simulation period in 2010, with 58% in soil organic matter, 22% in living biomass, and 20% in surface dead organic matter (litter and dead wood; Fig. 2a). Ecosystems accumulated carbon in all scenarios but at different rates, with trajectories shaped primarily by climate change and to a lesser extent by land-use change. The highest and most consistent projected accumulation of ecosystem carbon occured under the combination of low radiative forcing and low land use change, yielding a ~15% increase in ecosystem carbon to an average of 363 Tg by 2100 (Fig. 2a). In contrast, high radiative forcing and high land use change resulted in the lowest ecosystem carbon gain, reaching a peak of ~332 Tg in 2063 but declining to 327 Tg in 2100, resulting in a net increase of only 3% by the end of the simulation period (Fig. 2a). Ecosystem carbon accumulation was driven exclusively by increasing soil organic carbon across all four scenarios, all other stocks declined over time (Fig. 2b).

```{r fig.align = 'center', out.width = "99%", fig.cap = "Projected changes in total ecosystem carbon storage (a) and individual carbon stocks (b) for the seven main Hawaiian Islands. Solid lines indicate the mean of 30 Monte Carlo realizations for each scenario, with shaded areas indicating the minimum and maximum range of Monte Carlo realizations."}
knitr::include_graphics("./fig_images/fig2_Cstocks.png")
```
